Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks

### 2023-05-31 evaluation/evaluation.tex
Updates from Overleaf

\begin{figure}[ht]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
        \caption[]{first figure}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
        \caption[]{second figure}
    \end{minipage}
    \vfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
        \caption[]{third figure}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
        \caption[]{fourth figure}
    \end{minipage}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
        \caption[self-similarity matrix]{Self-similarity matrix visualizes the similarity of different parts of the audio feature to each other. It illustrates how each point in the feature space correlates with every other point, providing insights into structural patterns or repetitions in the audio.}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
        \caption[Self-similarity lag matrix]{A self-similarity lag matrix represents how similar each point in the feature space is with its 'lagged' or time-shifted versions. This provides insights into periodicity and temporal patterns within the audio data.}
    \end{minipage}
    \vfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
        \caption[Q-matrix]{The cumulative matrix uses a recursive process that maximizes previous values and adds the current value from the recurrence plot. The Q-matrix acts as a global similarity measure by considering all aligned sample matches throughout the time series without penalizing local disruptions or mismatches.}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
        \caption[Transitive Binary Similarity Matrix]{Transitive Binary Similarity Matrix identifies similarity relationships between different segments or points in the feature. This matrix aids in discovering recurrent patterns or structures within the audio feature.}
    \end{minipage}
\end{figure}

### 2023-05-31 results/results.tex
Updates from Overleaf

XXXXXXXXXXXXXXXXX

\input{figures/neural networks/manifold}

\section{Tables and graphics}

XXXXXXXXXXXXXXXXX

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
\caption[Graph.]{This is an example of a figure and its caption.}
\label{fig:timeseries}
\end{figure}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.50}
\caption[Table]{This is an example of a table and its caption.}
\label{tablePCA}
\centering
\begin{tabular}{| c | c | c | c | c |}
\hline
\bfseries PCA & \bfseries Residual mean & \bfseries XXX & \bfseries XXX & \bfseries XXX \\
\hline\hline
Original PCA & 0.1267 & XXX & XXX & XXX  \\
\hline
PCA on Centroid 1 & 0.1249 & XXX & XXX  & XXX\\
\hline
PCA on Centroid 2 & 0.1214  & XXX & XXX  & XXX\\
\hline
\end{tabular}
\end{table}

>>>>

\input{results/subsections/tables}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/first results.png}
    \caption{Caption}
    \label{fig:boxplotmetrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
    \caption{Caption}
    \label{fig:boxplotfmeasure}
\end{figure}

The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries. This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation. Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly. Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries. This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
